\speculake: Hiding Malware in Speculative Execution

### 2018-12-13 paper/figures.tex
fix typos

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{\textbf{Speculative limits}\,---\,%
    To find the number of instructions we can execute speculatively we placed a signal gadget
    after an increasing number of instructions and measured the fraction of times the 
    loaded value was subsequently in cache. We identify two limitation on the number of instructions
    accomplishable speculatively -- cache latency, and the CPU's reorder buffer~(ROB) size. We find that the
    hit fraction for instructions with a ratio of cycle latency to $\mu$~ops greater than 1 undergo a
    steep drop to \~0.1 hit fraction before falling definitively to 0. The drop in hit fraction 
    indicates that the duration of the test in cycles is beyond the fist step in cache latency as shown in 
    Figure~\ref{fig:cache-miss} (approx. 200 cycles). Whether or not the instruction sequence reaches the 
    cycle count limit we see only a sharp drop in hit fraction to 0 indicating the limiting factor 
    is ROB size. For example, the \texttt{idiv (r32)} instruction we identify 18 as the maximum number of 
    instruction limited by ROB (not including ~15 instructions for signal gadget), with a soft limit at 
    12 instructions enforced by the cache latency. We measure the ROB size by timing two cache 
    accesses with a variable number of instructions between them and note that this aligns with 
    the measured maximum \texttt{nop} instrustions.
    }
    \label{fig:spec-capacity-np}
\end{figure*}
}

>>>>

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{\textbf{Speculative limits}\,---\,% To find the number of
    instructions we can execute speculatively we placed a signal gadget after an
    increasing number of instructions and measured the fraction of times the
    loaded value was subsequently in cache. We identify two limitations on the
    number of instructions accomplishable speculatively: cache latency, and the
    CPU's reorder buffer~(ROB) size. We find that the hit fraction for
    instructions with a ratio of cycle latency to $\mu$~ops greater than 1
    undergo a steep drop to $\approx$ 0.1 hit fraction before falling
    definitively to 0. The drop in hit fraction indicates that the duration of
    the test in cycles is beyond the first step in cache latency as shown in
    Figure~\ref{fig:cache-miss} (approx. 200 cycles). Whether or not the
    instruction sequence reaches the cycle count limit we see only a sharp drop
    in hit fraction to 0 indicating the limiting factor is ROB size. For
    example, we identify 18 as the maximum number of \texttt{idiv (r32)}
    instructions computable speculatively, limited by ROB (not including
    $\approx$ 15 instructions for signal gadget), with a soft limit at 12
    instructions enforced by the cache latency. We measure the ROB size by
    timing two cache accesses with a variable number of instructions between
    them and note that this aligns with the measured maximum \texttt{nop}
    instrustions.}
    \label{fig:spec-capacity-np}
\end{figure*}
}
